---
title: "New York Airbnb Analysis"
output: html_notebook
---

```{r}
#Viewing and cleaning data after importing it into RStudio
head(airbnb)
data_unique=airbnb[!duplicated(airbnb),]
dt=na.omit(data_unique)
head(dt)
```


```{r}
#Quick Descriptive Statistics on Pricing and Rating
summary(dt$Price)
summary(dt$`Review Scores Rating`)
```

From the summary call, we see that the median price across all boroughs is $125.80. The minimum is $10, and the maximum is $10,000. Looking at the summary for Review Scores, the mean rating is 91.99, across all boroughs and property types. Let's take a look at the $10 residence and the $10,000 dollar residence.


```{r}
#Checking the airbnb with minimum pricing
dt[dt$Price=="10", ]

```

The place charging $10 is actually a house in Bronx called "Small Sofa", offering a shared one room. It has been available for booking since 2014 and has a rating of 100.


```{r}
#Checking the airbnb with maximum pricing.
dt[dt$Price=="10000", ]

```

The place charging $10,000 is an entire apartment in Manhattan offering two beds with a review score rating of 95. It has been on the market since 2014, although it looks like it is no longer accepting reservations.


```{r}
#Which borough contains the most locations for reservation?
library(ggplot2)
ggplot(dt, aes(x=Borough))+geom_bar(stat="count",fill="orange")+labs(title="Which borough contains the most locations for reservation?", y="Count")

```
Manhattan contains the most places for reservation, followed by Brooklyn, Queens, Bronx and Staten Island.


```{r}
#What are the property types in each borough?
ggplot(dt, aes(y=dt$`Property Type`))+geom_bar(stat="count",fill="turquoise")+labs(title="Property Types in Each Borough", y= "Property Type", x="Count")+facet_wrap(~Borough)
```

The property type most available across all boroughs are apartments, followed by houses,then lofts. It is interesting how apartments are the most common. This may be due to changes in social culture favoring temporal living habits.


```{r}
#What are the number of beds in each borough?
ggplot(dt, aes(x= Beds))+geom_bar(stat="count", fill="turquoise")+labs(title="Number of Beds Available in Each Borough", y= "Count", x="Beds")+facet_wrap(~Borough)
```
One bed spaces are most common in each borough as well, perhaps indicating the societal changes favoring temporal habits; or simply people wanting to rent their guest rooms for passive income.

```{r}
#What are the places sporting 16 beds?
dt[dt$Beds=="16", ]

```
On the other hand, 16 bed residences are commonly entire houses in Brooklyn, echoing a form of duration and stability compared to the one bed apartments.

```{r}
#Average Pricing in each of the boroughs

dt %>%
  group_by(Borough) %>%
  summarise(median_price = median(Price)) %>%
  ggplot(aes(x = factor(Borough), y = median_price)) +
  geom_col(fill="orange") +
  labs(x = "Borough", y = "Median Price", title = "Median Price Based on Borough")
```
Median prices are higher in Manhattan, followed by Brooklyn, Queens, Staten Island, and Bronx. Since median is less affected by extreme values(like the $10,000 Airbnb), it is best to utilize median to describe the central tendency of prices.


Conclusion:

Based on the analysis,it is evident that New York Airbnb median pricing depends on the borough. Locations in Manhattan and Brooklyn are most expensive. Furthermore, one bed apartments are most common in the market, across all boroughs. While this may be idle for solo travelers or couples, it may not be best for large families. Thus in this situation, Brooklyn may be best for accommodation.

